\documentclass{deedy_resume}

\begin{document}

% Header
\namesection{Diwakar Raj R}{
    \href{mailto:diwakarraj385@gmail.com}{diwakarraj385@gmail.com} | 9551331855 | Tiruvallur, Tamil Nadu - 602025
}{
    \href{https://github.com/diwakarraj}{GitHub} | \href{https://linkedin.com/in/diwakarraj}{LinkedIn} % Assuming standard links, user can update
}

% Education
\section{Education}
\runsubsection{Prathyusha Engineering College} \\
\descript{B.E - Computer Science and Engineering}
\location{09/2023 – Present | Tiruvallur, Tamil Nadu}
\sectionsep

\runsubsection{BharathiDasan Matriculation Hr Sec School} \\
\descript{Higher Secondary}
\location{07/2021 – 06/2023 | Tiruvallur, Tamil Nadu}
\sectionsep

\runsubsection{Chinni Sriramulu Chetty Vivekananda Vidhyalaya} \\
\descript{Matriculation}
\location{07/2008 – 05/2020 | Tiruvallur, Tamil Nadu}
\sectionsep

% Skills
\section{Skills}
\begin{tightemize}
    \item \textbf{Languages \& Frameworks:} C, Java, Python, Dart, React, HTML/CSS
    \item \textbf{Tools & Platforms:} Git, GitHub, Figma, Blender, Unity, Excel
    \item \textbf{Domains:} Web Development, UI/UX Design, AR/VR, 3D Modelling
\end{tightemize}
\sectionsep

% Experience
\section{Professional Experience}
\runsubsection{Unstop} \\
\descript{Campus Leader}
\location{08/2025 – Present | Tiruvallur}
\begin{tightemize}
    \item Selected as a campus leader to be the primary liaison between Unstop and Prathyusha Engineering College.
    \item Built and managed a student community, organizing workshops and hackathons.
    \item Drove competition participation via social media and club collaborations.
\end{tightemize}
\sectionsep

\runsubsection{Google Gemini} \\
\descript{Campus Ambassador}
\location{08/2025 – Present | Tiruvallur}
\begin{tightemize}
    \item Selected as Google Gemini Student Ambassador, leading a 6-month program to build a campus AI community.
    \item Organized workshops, training students in AI for coding and research.
    \item Acted as the primary student-Google liaison, providing direct community feedback.
\end{tightemize}
\sectionsep

% Projects
\section{Projects}
\runsubsection{Mathsol - The Mathematical Formula Calculator} \\
\descript{Web Application}
\location{06/2024 – 08/2024}
\begin{tightemize}
    \item Open-source, client-side platform built with HTML, CSS, and JavaScript.
    \item Provides instant, step-by-step solutions for algebra, calculus, and matrix operations.
    \item Designed for students to practice math and understand concepts without server interaction.
\end{tightemize}
\sectionsep

\runsubsection{Simple Calculator} \\
\descript{Basic Application}
\location{12/2023 – 12/2023}
\begin{tightemize}
    \item Developed a basic calculator interface for instant addition, subtraction, multiplication, and division.
    \item Used as an educational example for programming fundamentals.
\end{tightemize}
\sectionsep

% Achievements
\section{Achievements}
\begin{tightemize}
    \item \textbf{Google Gemini Student Ambassador:} Led AI community building initiatives and workshops.
    \item \textbf{Unstop Campus Ambassador:} Managed student community and organized hackathons.
\end{tightemize}
\sectionsep

% Certificates
\section{Certificates}
\begin{tightemize}
    \item Database Management System
    \item UI / UX For Beginners
    \item Mobile Virtual Reality and Artificial Intelligence
    \item GenAI Study Jam (Google Cloud)
    \item Intro to Graphic Design with Photoshop
\end{tightemize}
\sectionsep

\end{document}
